---
title: "Kermit Perceptions Rank-based Tests"
author: "Jamie K. Miller"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

JKM's first message in document


Hello. Adding some fun words.


JKM: yay more fun words! yada yada yada. so professional.

```{r}
library("tidyverse")
kermit <- read_csv("kermit.csv")

kermit_hist <-ggplot(kermit, aes(x= Score.pre)) +
  geom_histogram(bins = 4)+
  facet_wrap(~Gender)
kermit_hist

```
Creator: Perform rank-based comparisons using MNann-Whitney U and Wilcoxon-Signed Rank

Question: Is ther a significant difference in pre-talk ranks of Kermit for Male and Female respondents?

```{r}

mwu_kermit <- kermit %>%
  wilcox.test(Score.pre ~ Gender, data = .)

# H0: There is NO significant difference in ranks for male and female respondents
# HA: There is a significant difference in ranks for male and female respondents

mwu_kermit
```

"There was no significant difference in ranks for male and female respondents (W = 155.5, p = 0.45, alpha = 0.05)."



Is there a signif  change in Kermit rankings before and after his Bren talk? Ack one-to-one relationship between the values.

```{r}
wsr_kermit <-wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

wsr_kermit
```

There is no significant difference. 







